%------------------------
% AI-Optimized Resume Template
%------------------------

\documentclass[letterpaper,11pt]{article}

\usepackage{latexsym}
\usepackage[empty]{fullpage}
\usepackage{titlesec}
\usepackage{marvosym}
\usepackage[usenames,dvipsnames]{color}
\usepackage{verbatim}
\usepackage{enumitem}
\usepackage[pdftex]{hyperref}
\usepackage{fancyhdr}
\usepackage{fontawesome}

\pagestyle{fancy}
\fancyhf{}
\fancyfoot{}
\renewcommand{\headrulewidth}{0pt}
\renewcommand{\footrulewidth}{0pt}

% Margins
\addtolength{\oddsidemargin}{-0.375in}
\addtolength{\evensidemargin}{-0.375in}
\addtolength{\textwidth}{1in}
\addtolength{\topmargin}{-.5in}
\addtolength{\textheight}{0.8in}

\urlstyle{same}
\raggedbottom
\raggedright
\setlength{\tabcolsep}{0in}

% Section formatting
\titleformat{\section}{
  \vspace{-1pt}\scshape\raggedright\large\bfseries
}{}{0em}{}[\color{black}\titlerule \vspace{-2pt}]

% Commands
\newcommand{\email}[1]{\faEnvelope\ \href{mailto:#1}{#1}}
\newcommand{\linkedin}[2][]{\faLinkedin\ \href{#2}{#1}}
\newcommand{\github}[2][]{\faGithub\ \href{#2}{#1}}
\newcommand{\website}[2][]{\faGlobe\ \href{#2}{#1}}
\newcommand{\name}[1]{ \centerline{\Huge\scshape\bfseries{#1}} }

\newcommand{\resumeSubheading}[4]{
  \vspace{-1pt}\item
    \begin{tabular*}{0.97\textwidth}{l@{\extracolsep{\fill}}r}
      \textbf{#1} & #2 \\
      \textit{\small#3} & \textit{\small #4} \\
    \end{tabular*}\vspace{-2pt}
}

\newcommand{\resumeCompanyHeader}[2]{
  \vspace{-1pt}\item
    \begin{tabular*}{0.97\textwidth}{l@{\extracolsep{\fill}}r}
      \textbf{#1} & #2 \\
    \end{tabular*}\vspace{-2pt}
}

\newcommand{\resumeJobTitle}[2]{
  \vspace{-2pt}\item
    \begin{tabular*}{0.97\textwidth}{l@{\extracolsep{\fill}}r}
      \textit{\small\bfseries#1} & \textit{\small #2} \\
    \end{tabular*}\vspace{-2pt}
}

\newcommand{\project}[1]{
  \vspace{-1pt}\item
  \textbf{#1}\vspace{-4pt}
}

\newcommand{\resumeBullet}[1]{\item\small{#1}}

\newcommand{\resumeItemListStart}{\begin{itemize}[leftmargin=*, label={}]}
\newcommand{\resumeItemListEnd}{\end{itemize}}

\newcommand{\resumeBulletStart}{
  \begin{itemize}[leftmargin=*, itemsep=3pt, topsep=3pt]
}
\newcommand{\resumeBulletEnd}{\end{itemize}}

\begin{document}

% HEADER
\name{Lucas Hope}
\begin{center}
    \email{lucasfhope@icloud.com} \textperiodcentered\
    \website[lucashope.xyz]{https://lucashope.xyz}
    \textperiodcentered\
    \linkedin[lucashope]{https://www.linkedin.com/in/lucashope/}
    \textperiodcentered\
    \github[lucash0pe]{https://github.com/lucash0pe}
\end{center}

% EDUCATION
\section{Education}
\resumeItemListStart
  \resumeSubheading
    {Stevens Institute of Technology}{Hoboken, NJ}
    {BS in Computer Science (GPA: 3.7)}{September 2021 -- December 2024}
\resumeItemListEnd

% EXPERIENCE
\section{Experience}
\resumeItemListStart

  \resumeCompanyHeader{Jersey Mike's Subs}{Wall, NJ}
  \resumeJobTitle{AI Application Engineer}{May 2025 -- Present}
  \resumeBulletStart
    \resumeBullet{
      Built a natural language sales analytics system that converts business questions into validated, schema-driven execution pipelines using structured LLM outputs.
    }
    \resumeBullet{
      Implemented a deterministic query execution framework supporting filtering, grouping, aggregation, and sorting across the dataset, with strict validation of dimensions and metrics.
    }
    \resumeBullet{
      Rapidly prototyped and presented MVP analytics tools to business stakeholders, iterating on feedback to align technical capabilities with business needs.
    }
  \resumeBulletEnd

  \resumeJobTitle{Data Engineering Intern}{Summer 2023, 2024}
  \resumeBulletStart
    \resumeBullet{
      Engineered Playwright-based automation to collect competitor pricing across key markets, implementing strategies to navigate anti-bot protections and eliminating 4 days of manual data collection per month.
    }
    \resumeBullet{
      Designed data ingestion workflows to normalize and store scraped pricing data in PostgreSQL for downstream analytics.
    }
    \resumeBullet{
      Prototyped LLM-assisted insight generation workflows to analyze pricing trends and support competitive strategy reporting.
    }
  \resumeBulletEnd

\resumeItemListEnd

% PROJECTS
\section{Projects}
\resumeItemListStart

  \project{Web3 Security Portfolio}
  \resumeBulletStart
    \resumeBullet{
      Analyzed smart contract vulnerabilities including reentrancy, flash loan exploits, and access control flaws across DeFi protocols.
    }
    \resumeBullet{
      Produced detailed exploit walkthroughs and mitigation strategies based on competitive audits and security challenges.
    }
  \resumeBulletEnd

  \project{ExtendedSQL}
  \resumeBulletStart
    \resumeBullet{
      Designed and implemented a SQL-like query engine to support complex aggregation across dynamic grouping dimensions, including parsing, execution planning, and evaluation logic.
    }
  \resumeBulletEnd

\resumeItemListEnd

% SKILLS
\section{Skills and Technologies}
\resumeItemListStart
  \item\small{
    \textbf{Programming Languages:} Python, SQL, TypeScript, JavaScript, Solidity, Rust, Go \\
    \textbf{Frameworks \& Tools:} FastAPI, Flask, React, LangGraph, Pydantic, Foundry, OpenWebUI, LaTeX, RAG Pipelines \\
    \textbf{Data \& Infrastructure:} PostgreSQL, AWS, Docker, Git, Linux, Vector Databases
  }
\resumeItemListEnd

% LEADERSHIP
\section{Leadership}
\resumeItemListStart
  \resumeSubheading
    {Alpha Sigma Phi – Alpha Tau Chapter}{}{President}{}
  \resumeBulletStart
    \resumeBullet{
      Led a 40-member organization and directed a 10-officer executive board.
    }
    \resumeBullet{
      Managed chapter operations, strategic planning, and coordination with university administration and national leadership.
    }
  \resumeBulletEnd
\resumeItemListEnd

\end{document}

